\addcontentsline{toc}{chapter}{Acknowledgment}

\begin{center}
\huge{{\bf Acknowledgments}}
\vspace{4cm}
\end{center}

I would like to express my heartfelt gratitude to the following individuals and institutions who have played a significant role in shaping me into the person I am today:

First and foremost, my beloved mother, whose support and belief in my potential has been my guiding light throughout my life. Her invaluable lessons on dedication, patience, and discipline have helped me overcome countless challenges and achieve my goals.

I also extend my gratitude to my father, whose teachings on the virtues of ambition have inspired me to strive for excellence. His relentless pursuit of success has been a constant source of energy for me.

I would like to acknowledge the outstanding education and training that I received from UFMG, which has equipped me with the necessary skills and knowledge to thrive in the global marketplace. I am grateful for the transformative experience that has prepared me for a fulfilling career and a meaningful life.

Moreover, I cannot forget my dear friends from República Casassanta, who have made my student life such a unique and unforgettable moment. Their camaraderie and support have been a source of joy and comfort during challenging times.

Lastly, I would like to thank myself for having the courage and resilience to pursue my dreams despite my anxieties and doubts. Through my perseverance, I have been able to savor every moment of my journey and give my best to achieve my goals.


\clearpage
\thispagestyle{empty}
\cleardoublepage